### 2017-04-03 paper/evaluation.tex
minor fixes

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\footnote{As of now, \github{}'s
  search API can only reflect contents from README file (not other
  code elements).}.  We focused on Java for its popularity.  Although
there is no clearcut limit on number of \github{}
stars~\cite{github-stars} to define an interesting project, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria is a constraint to skip projects without recent activity. The
fourth criteria is an approximation to find Maven projects. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or test the
project). We used Maven as a reference due to its popularity on Java
projects and to automate our evaluation scripts. A Maven project may
contain several sub-modules with multiple \pomf{} files. We considered
only projects with a \pomf{} file located in the root directory.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven (or did not have a \pomf{} in the root
directory) and \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example). To ensure that our sample set was stable, we retested
the remaining subjects to eliminate flaky tests (total of
\SubjectsGithubFlaky{} subjects). Our final set consists in
\numSubjs{} testable subjects.

>>>>

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\footnote{As of now, \github{}'s
  search API can only reflect contents from README file (not other
  code elements).}.  We focused on Java for its popularity.  Although
there is no clearcut limit on number of \github{}
stars~\cite{github-stars} to define an interesting project, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria is a constraint to skip projects without recent activity. The
fourth criteria is an approximation to find Maven projects. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or to test the
project). We used Maven as a reference due to its popularity on Java
projects and to assist one of our experiments. A Maven project may
contain several sub-modules with multiple \pomf{} files but we only
considered projects with a \pomf{} file located in the root directory.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory and \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example). To ensure that our sample set was stable, we retested
the remaining subjects to eliminate projects with flaky tests (total of
\SubjectsGithubFlaky{} subjects). Our final set consists of
\numSubjs{} testable subjects.
